Non-kissing complexes for gentle algebras

### 2020-06-29 firstPaper/FPSAC/nonKissingComplexFPSACRevision.tex
FPSAC

%% if you are submitting an initial manuscript then you should have submission as an option here
%% if you are submitting a revised manuscript then you should have revision as an option here
%% otherwise options taken by the article class will be accepted
\documentclass[finalversion]{FPSAC2018}
\articlenumber{39}
%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc

@@

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{1},
	\stepcounter{footnote}
	Vincent Pilaud\thanks{\href{mailto:}{vincent.pilaud@lix.polytechnique.fr}. Supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}\addressmark{2}, \and
	Pierre-Guy Plamondon\addressmark{3}\thanks{\href{mailto:}{pierre-guy.plamondon@math.u-psud.fr}. Supported by French the ANR grant SC3A~(15\,CE40\,0004\,01).}
}

@@

%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
%% but you can use bibtex if you want
\usepackage[backend=bibtex]{biblatex}
\addbibresource{nonKissingComplexFPSAC.bib}
%% note the \printbibliography command at the end of the file which goes with these biblatex commands

@@

The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Section~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Theorem 1.1, Section~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
As already observed in~\cite[Section~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron, and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
In particular, the straight ribbon corresponds to the Tamari lattice, an object at the heart of a deep research area~\cite{TamariFestschrift}.
When the shape is a rectangle (or even a staircase), the non-kissing complex was studied in~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker} as the Grassmann associahedron, in connection to non-crossing subsets of~$[n]$.

@@

The precise statement and the proof of Theorem~\ref{thm:motivation} can be found in the long version of this paper~\cite{PaluPilaudPlamondon}, as well as further representation-theoretic aspects of the project.
In this extended abstract, we focus on combinatorial and geometric aspects.
We first define in Section~\ref{sec:nonkissingcomplex} the non-kissing complex of a gentle bound quiver and show that this complex is a pseudomanifold (meaning in particular that there is a well-defined notion of flips in non-kissing facets).
In Section~\ref{sec:nonkissinglattice}, we show that the graph of increasing flips is the Hasse diagram of a congruence-uniform lattice and describe its canonical join complex.
Finally, Section~\ref{sec:gentleAssociahedra} is devoted to the geometry of finite non-kissing complexes: we construct their $\b{g}$-vector fans and show that these fans are normal fans of convex polytopes.
We refer to~\cite{PaluPilaudPlamondon} for detailed proofs and further properties of non-kissing complexes.

@@

We fix a \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$, where~$Q \eqdef (Q_0, Q_1, s, t)$ is a \defn{quiver} with vertices~$Q_0$, arrows~$Q_1$, and source and target maps~$s, t : Q_1 \to Q_0$, and~$I$ is a set of quadratic \defn{relations}~$\alpha\beta = 0$ with~$\alpha, \beta \in Q_1$ and~$t(\alpha) = s(\beta)$ such that for any~$\beta \in Q_1$ there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$ (resp.~$\alpha\beta \notin I$) and at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$~(resp.~${\beta\gamma \notin I}$).
See Figure~\ref{fig:exmQuiver}.
In all pictures, a relation~$\alpha\beta = 0$ is indicated with an arc connecting the target of~$\alpha$ to the source of~$\beta$.

@@

The \defn{blossoming quiver} of~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ obtained by adding arrows and relations at each vertex~$v \in Q_0$, so that~$v$ has precisely $2$ incoming and $2$ outgoing arrows and still fulfills the gentle conditions. See Figure~\ref{fig:exmQuiver}.

\begin{figure}[b]
	\centerline{\includegraphics[scale=.6]{exmQuiver}}
	\caption{A gentle bound quiver~$\bar Q$ (left), its blossoming quiver~$\bar Q\blossom$ (middle), and some walks in~$\bar Q\blossom$ (right). The dotted red and orange walks are non-kissing, but both are kissing the plain blue walk. See Figure~\ref{fig:exmFlip} for examples of non-kissing facets.}
	\label{fig:exmQuiver}
\end{figure}

@@

Consider two walks~$\omega,\omega'$ on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exists a common substring~$\sigma$ of~$\omega$ and~$\omega'$ such that~$\omega$ has two outgoing arrows incident to~$\sigma$ while~$\omega'$ has two incoming arrows incident to~$\sigma$.
See Figures~\ref{fig:exmQuiver}\,(right)~\&~\ref{fig:kissingFlip}\,(left).
We authorize the case where~$\sigma$ is reduced to a vertex~$v$, \ie~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Note that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of walks which are not self-kissing and pairwise non-kissing.
Note that no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
See Figure~\ref{fig:exmNKC}\,(left).

Our definition of non-kissing complex is largely inspired from and specializes to simplicial complexes defined from subsets of the grid~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} or from dissections of polygons~\cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion}. 
To the best of our knowledge, we actually provide the first connection between these two families, besides the observation that associahedra are instances of both.
In fact, the example of Figure~\ref{fig:exmNKC} is also a special case of both families.

@@

A \defn{marked walk}~$\omega_\star$ is a walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ with a marked arrow~$\alpha_i^{\varepsilon_i}$.
Consider two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an arrow~$\alpha^\varepsilon \in Q\blossom_1$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction of~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the opposite direction.
For a face~$F$ of~$\NKC$, we call \defn{distinguished walk} of~$F$ at an arrow~$\alpha$ the $\prec_\alpha$-maximal walk~$\distinguishedWalk{\alpha}{F}$, and we call \defn{distinguished arrows} of a walk~$\omega \in F$ the arrows~$\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}$.
The following statement is inspired from~\cite[Theorem~3.2]{McConville} and illustrated in Figure~\ref{fig:exmFlip}\,(left).

@@

\begin{proposition}
\label{prop:flip}
Consider a facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
Write~${\omega = \rho \sigma \tau}$ where~$\sigma \eqdef \distinguishedString{\omega}{F}$.
%The distinguished substring~$\sigma = \distinguishedString{\omega}{F}$ splits~$\omega$ into~${\omega = \rho \sigma \tau}$.
Let~$\{\alpha, \beta\} \eqdef \distinguishedArrows{\omega}{F}$, and~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~${\alpha'\alpha \in I}$ or~${\alpha\alpha' \in I}$, and ${\beta'\beta \in I}$ or~${\beta\beta' \in I}$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
See Figures~\ref{fig:kissingFlip}\,(right) \&~\ref{fig:exmFlip}.~Then
\begin{compactenum}[(i)]
\item The string~$\sigma$ splits the walk~$\mu$ into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{compactenum}
We say that~$F \symdif \{\omega, \omega'\}$ is obtained from~$F$ by \defn{flipping}~$\omega$, and that the flip is \defn{supported}~by~$\sigma$.
\end{proposition}

@@

The flip of Proposition~\ref{prop:flip} and Figures~\ref{fig:kissingFlip} \&~\ref{fig:exmFlip} exchanges two kissing walks~$\omega, \omega'$.
The~flip is \defn{increasing} when their common substring is on top of~$\omega$ and on the bottom of~$\omega'$.
This yields the \defn{increasing flip graph}, where vertices are non-kissing facets and arcs are increasing flips.
%The \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ is a source and the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$ is a sink.
See Figure~\ref{fig:exmNKC}\,(right).
The main result of this section is the following~statement.

@@

Congruence-uniform lattices will be properly defined in Section~\ref{subsec:joinRepresentations}.
To achieve Theorem~\ref{thm:lattice}, we use a technique developed by T.~McConville for grid quivers~\cite{McConville}: we identify the non-kissing lattice with a quotient of a lattice of biclosed sets of strings.

@@

A \defn{closure operator} on a finite set~$\cS$ is a map~$S \mapsto \closure{S}$ on subsets of~$\cS$ such that~$\closure{\varnothing} = \varnothing$, $S \subseteq \closure{S}$, $\closure{(\closure{S})} = \closure{S}$ and~$S \subseteq T \Longrightarrow \closure{S} \subseteq \closure{T}$ for any~$S,T \subseteq \cS$.
A subset~${S \subseteq \cS}$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
Let~$\Bicl{\cS}$ be the inclusion poset of biclosed subsets of~$\cS$.
In~\cite[Theorem~5.5]{McConville}, T.~McConville gave simple sufficient conditions for~$\Bicl{\cS}$ to be a congruence uniform lattice.
In~\cite[Theorem~3.21]{PaluPilaudPlamondon}, we extended this criterion in the situation when the singletons of~$\cS$ are not biclosed so that we can apply it in our context of non-kissing complexes.

In a gentle bound quiver~$\bar Q$, we define the \defn{closure}~$\closure{S}$ of a set~$S$ of strings of~$\bar Q$ as the set of all strings of the form~$\sigma_1 \alpha_1^{\varepsilon_1} \sigma_2 \alpha_2^{\varepsilon_2} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$ where~$\sigma_i \in S, \alpha_i \in Q_1$ and~${\varepsilon_i \in \{-1,1\}}$.
Let~$\Bicl{\bar Q}$ be the inclusion poset on biclosed sets of strings of~$\bar Q$.
For example, when~$\bar Q$ is a path on $n$ vertices with no relation, the strings are in bijection with pairs~${(i,j) \in \binom{n+1}{2}}$, the closure on strings translates to the concatenation~${(i,j) \circ (k,\ell) = \delta_{j = k} (i, \ell)}$, biclosed sets of strings are in bijection with inversion sets of permutations of~$[n+1]$, so that~$\Bicl{\bar Q}$ is isomorphic to the weak order on~$\fS_{n+1}$.
Figure~\ref{fig:exmLatticeQuotient}\,(left) illustrates the poset~$\Bicl{\bar Q}$ for another gentle bound quiver, with the empty set in the bottom and the set of all strings of~$\bar Q$ on top. The criterion of~\cite[Theorem~3.21]{PaluPilaudPlamondon} yields the following~result.

@@

Following~\cite[Section~7]{McConville}, we associate to a biclosed set~$S \in \Bicl{\bar Q}$ the sets \\[.1cm]
\centerline{$
\projDown(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S}
\quad\text{and}\quad
\projUp(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
$} \\[.1cm]
Here and throughout the paper, we denote by~$\Sigma_\bottom(\sigma)$ the set of bottom substrings for a string ${\sigma = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}}$, \ie the substrings~$\alpha_m^{\varepsilon_m} \dots \alpha_n^{\varepsilon_n}$ for $1 \le m \le n \le \ell$ such that~$m = 1$ or~$\varepsilon_{m-1} = -1$, and $n = \ell$ or $\varepsilon_{n+1} = 1$ (and similarly for the set of top substrings~$\Sigma_\top(\sigma)$).

@@

For example, if~$\bar Q$ is an oriented path with no relation, $\equiv$ is a Cambrian congruence of the weak~order~\cite{Reading-CambrianLattices}.
The congruence classes of~$\equiv$ appear as blue rectangles~in~Figure~\ref{fig:exmLatticeQuotient}.

@@

Coming back to our original problem, we now aim to show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the quotient of the lattice of biclosed set~$\Bicl{\bar Q}$ of Section~\ref{subsec:biclosedSets} by the lattice congruence of Section~\ref{subsec:congruence}.
The next two propositions provide explicit maps between biclosed sets of strings and non-kissing facets illustrated in Figure~\ref{fig:exmSurjection}. It extends previous definitions of~\cite{McConville} for grid quivers.

@@

\begin{proposition}
For any facet~$F \in \NKC$, the set~$\zeta(F) \eqdef \displaystyle\closure{\Big( \bigcup\limits_{\omega \in F} \Sigma_\bottom(\omega) \Big)}
$~is~biclosed.
\end{proposition}

When the quiver is an oriented path with no relation, the map~$\eta$ should be thought of as the map from permutations to triangulations defined in~\cite{Reading-CambrianLattices}.
Conversely, $\zeta$ maps a triangulation to the minimal permutation in its fiber under~$\eta$.
For the straight quiver, $\eta$ plays the role of the binary search tree insertion while~$\zeta$ selects the minimal linear extension of a binary tree.
%
Using these maps, we show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$.

>>>>

%% if you are submitting an initial manuscript then you should have submission as an option here
%% if you are submitting a revised manuscript then you should have revision as an option here
%% otherwise options taken by the article class will be accepted
\documentclass[submission]{FPSAC2018Revision}
%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc

@@

% theorems
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{Yann Palu\addressmark{1}, Vincent Pilaud\addressmark{2} \and Pierre-Guy Plamondon\addressmark{3}\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}, \href{mailto:}{vincent.pilaud@lix.polytechnique.fr}, \href{mailto:}{pierre-guy.plamondon@math.u-psud.fr}. The three authors were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}}

@@

%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
%% but you can use bibtex if you want
\usepackage[backend=bibtex]{biblatex}
\addbibresource{nonKissingComplexFPSACRevision.bib}
%% note the \printbibliography command at the end of the file which goes with these biblatex commands

@@

The non-kissing complex is a simplicial complex of pairwise non-kissing paths in a fixed shape of a grid.
It was introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary shapes.
This complex is known to be a simplicial sphere, and it was actually realized as a polytope using successive edge stellations and suspensions in~\cite[Sect.~4]{McConville}.
Moreover, the dual graph of the non-kissing complex has a natural orientation which equips its facets with a lattice structure~\cite[Thm. 1.1, Sect.~5--8]{McConville}.
Further lattice theoretic and geometric aspects of this complex were recently developed by A.~Garver and T.~McConville in~\cite{GarverMcConville-grid}.

The interest for non-kissing complexes is motivated by relevant instances arising from particular shapes.
As already observed in~\cite[Sect.~10]{McConville}, when the shape is a ribbon, the non-kissing complex is an associahedron, and the non-kissing lattice is a type~$A$ Cambrian lattice of N.~Reading~\cite{Reading-CambrianLattices}.
In particular, the straight ribbon corresponds to the Tamari lattice, an object at the heart of a deep research area~\cite{TamariFestschrift}.
When the shape is a rectangle (or even a staircase), the non-kissing complex was studied in~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker} as the Grassmann associahedron, in connection to non-crossing subsets of~$[n]$.

@@

The precise statement and the proof of Theorem~\ref{thm:motivation} can be found in the long version of this paper~\cite{PaluPilaudPlamondon}, as well as further representation-theoretic aspects of the project.
In this extended abstract, we focus on combinatorial and geometric aspects.
We first define in Sec.~\ref{sec:nonkissingcomplex} the non-kissing complex of a gentle bound quiver and show that this complex is a pseudomanifold (meaning in particular that there is a well-defined notion of flips in non-kissing facets).
In Sec.~\ref{sec:nonkissinglattice}, we show that the graph of increasing flips is the Hasse diagram of a congruence-uniform lattice and describe its canonical join complex.
Finally, Sec.~\ref{sec:gentleAssociahedra} is devoted to the geometry of finite non-kissing complexes: we construct their $\b{g}$-vector fans and show that these fans are normal fans of convex polytopes.
We refer to~\cite{PaluPilaudPlamondon} for detailed proofs and further properties of non-kissing complexes.

@@

We fix a \defn{gentle bound quiver}~$\bar Q \eqdef (Q,I)$, where~$Q \eqdef (Q_0, Q_1, s, t)$ is a \defn{quiver} with vertices~$Q_0$, arrows~$Q_1$, and source and target maps~$s, t : Q_1 \to Q_0$, and~$I$ is a set of quadratic \defn{relations}~$\alpha\beta = 0$ with~$\alpha, \beta \in Q_1$ and~$t(\alpha) = s(\beta)$ such that for any~$\beta \in Q_1$ there is at most one~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~$\alpha\beta \in I$ (resp.~$\alpha\beta \notin I$) and at most one~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$ and~$\beta\gamma \in I$~(resp.~${\beta\gamma \notin I}$).
See Fig.~\ref{fig:exmQuiver}.
In all pictures, a relation~$\alpha\beta = 0$ is indicated with an arc connecting the target of~$\alpha$ to the source of~$\beta$.

@@

The \defn{blossoming quiver} of~${\bar Q = (Q,I)}$ is the gentle bound quiver~$\bar Q\blossom = (Q\blossom, I\blossom)$ obtained by adding arrows and relations at each vertex~$v \in Q_0$, so that~$v$ has precisely $2$ incoming and $2$ outgoing arrows and still fulfills the gentle quiver conditions. See Fig.~\ref{fig:exmQuiver}.

\begin{figure}[b]
	\centerline{\includegraphics[scale=.6]{exmQuiver}}
	\caption{A gentle bound quiver~$\bar Q$ (left), its blossoming quiver~$\bar Q\blossom$ (middle), and some walks in~$\bar Q\blossom$ (right). The dotted red and orange walks are non-kissing, but both are kissing the plain blue walk. See Fig.~\ref{fig:exmFlip} for examples of non-kissing facets.}
	\label{fig:exmQuiver}
\end{figure}

@@

Consider two walks~$\omega,\omega'$ on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$, \ie if there exists a common substring~$\sigma$ of~$\omega$ and~$\omega'$ such that~$\omega$ has two outgoing arrows incident to~$\sigma$ while~$\omega'$ has two incoming arrows incident to~$\sigma$.
See Figs.~\ref{fig:exmQuiver}\,(right)~\&~\ref{fig:kissingFlip}\,(left).
Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of walks which are not self-kissing and pairwise non-kissing.
Note that no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
See Fig.~\ref{fig:exmNKC}\,(left).

Our definition of non-kissing complex is largely inspired from and specializes to relevant simplicial complexes defined from subsets of the grid~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville-grid} or from dissections of polygons~\cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion}. 
To the best of our knowledge, we actually provide the first connection between these two families, besides the observation that associahedra are instances of both.
In fact, the example of Fig.~\ref{fig:exmNKC} is also a special case of both families.

@@

A \defn{marked walk}~$\omega_\star$ is a walk~$\omega = \alpha_1^{\varepsilon_1} \cdots \alpha_\ell^{\varepsilon_\ell}$ with a marked arrow~$\alpha_i^{\varepsilon_i}$.
Consider two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an arrow~$\alpha^\varepsilon \in Q\blossom_1$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction of~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the opposite direction.
For a face~$F$ of~$\NKC$, we call \defn{distinguished walk} of~$F$ at an arrow~$\alpha$ the $\prec_\alpha$-maximal walk~$\distinguishedWalk{\alpha}{F}$, and we call \defn{distinguished arrows} of a walk~$\omega \in F$ the arrows~$\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}$.
The following statement is inspired from~\cite[Thm.~3.2]{McConville} and illustrated in Fig.~\ref{fig:exmFlip}\,(left).

@@

\begin{proposition}
\label{prop:flip}
Consider a facet~$F \in \NKC$ and a bending walk~$\omega \in F$.
The distinguished substring~$\sigma = \distinguishedString{\omega}{F}$ splits~$\omega$ into~${\omega = \rho \sigma \tau}$.
Let~$\{\alpha, \beta\} \eqdef \distinguishedArrows{\omega}{F}$, and~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~${\alpha'\alpha \in I}$ or~${\alpha\alpha' \in I}$, and ${\beta'\beta \in I}$ or~${\beta\beta' \in I}$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$.
See Figs.~\ref{fig:kissingFlip}\,(right)~and~\ref{fig:exmFlip}.~Then
\begin{compactenum}[(i)]
\item The string~$\sigma$ splits the walk~$\mu$ into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{compactenum}
We say that~$F \symdif \{\omega, \omega'\}$ is obtained from~$F$ by \defn{flipping}~$\omega$, and that the flip is \defn{supported}~by~$\sigma$.
\end{proposition}

@@

The flip operation of Prop.~\ref{prop:flip} and Figs.~\ref{fig:kissingFlip} \&~\ref{fig:exmFlip} exchanges two kissing walks~$\omega, \omega'$.
The flip is \defn{increasing} when their common substring is on top of~$\omega$ and on the bottom of~$\omega'$.
This yields the \defn{increasing flip graph}, where vertices are non-kissing facets and arcs are increasing flips.
%The \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ is a source and the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$ is a sink.
See Fig.~\ref{fig:exmNKC}\,(right).
The main result of this section is the following statement.

@@

Congruence-uniform lattices will be properly defined in Sec.~\ref{subsec:joinRepresentations}.
To achieve Thm.~\ref{thm:lattice}, we use a technique developed by T.~McConville for grid quivers~\cite{McConville}: we identify the non-kissing lattice with a quotient of a lattice of biclosed sets of strings.

@@

A \defn{closure operator} on a finite set~$\cS$ is a map~$S \mapsto \closure{S}$ on subsets of~$\cS$ such that~$\closure{\varnothing} = \varnothing$, $S \subseteq \closure{S}$, $\closure{(\closure{S})} = \closure{S}$ and~$S \subseteq T \Longrightarrow \closure{S} \subseteq \closure{T}$ for any~$S,T \subseteq \cS$.
A subset~$S \subseteq \cS$ is \defn{closed} if~$\closure{S} = S$, \defn{coclosed} if~$\cS \ssm S$ is closed, and \defn{biclosed} if it is both closed and coclosed.
We denote by~$\Bicl{\cS}$ the inclusion poset of biclosed subsets of~$\cS$.
In~\cite[Thm.~5.5]{McConville}, T.~McConville provided simple sufficient conditions for~$\Bicl{\cS}$ to be a congruence uniform lattice.
In~\cite[Thm.~3.21]{PaluPilaudPlamondon}, we extended this criterion in the situation when the singletons of~$\cS$ are not biclosed so that we can apply it in our context of non-kissing complexes.

In a gentle bound quiver~$\bar Q$, we define the \defn{closure}~$\closure{S}$ of a set~$S$ of strings of~$\bar Q$ as the set of all strings of the form~$\sigma_1 \alpha_1^{\varepsilon_1} \sigma_2 \alpha_2^{\varepsilon_2} \dots \alpha_{\ell-1}^{\varepsilon_{\ell-1}} \sigma_\ell$ where~$\sigma_i \in S, \alpha_i \in Q_1$ and~${\varepsilon_i \in \{-1,1\}}$.
Let~$\Bicl{\bar Q}$ be the inclusion poset on biclosed sets of strings of~$\bar Q$.
For example, when~$\bar Q$ is a path on $n$ vertices with no relation, the strings are in bijection with pairs~${(i,j) \in \binom{n+1}{2}}$, the closure on strings translates to the concatenation~${(i,j) \circ (k,\ell) = \delta_{j = k} (i, \ell)}$, biclosed sets of strings are in bijection with inversion sets of permutations of~$[n+1]$, so that~$\Bicl{\bar Q}$ is isomorphic to the weak order on~$\fS_{n+1}$.
Fig.~\ref{fig:exmLatticeQuotient}\,(left) illustrates the poset~$\Bicl{\bar Q}$ for another gentle bound quiver, with the empty set in the bottom and the set of all strings of~$\bar Q$ on top. The criterion of~\cite[Thm.~3.21]{PaluPilaudPlamondon} yields the following~result.

@@

Following~\cite[Sect.~7]{McConville}, we associate to a biclosed set~$S \in \Bicl{\bar Q}$ the sets \\[.1cm]
\centerline{$
\projDown(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\bottom(\sigma) \subseteq S}
\quad\text{and}\quad
\projUp(S) \eqdef \set{\sigma \in \strings(\bar Q)}{\Sigma_\top(\sigma) \cap S \ne \varnothing}.
$} \\[.1cm]
Here and throughout the paper, we denote by~$\Sigma_\bottom(\sigma)$ the set of bottom substrings for a string ${\sigma = \alpha_1^{\varepsilon_1} \dots \alpha_\ell^{\varepsilon_\ell}}$, \ie the substrings~$\alpha_m^{\varepsilon_m} \dots \alpha_n^{\varepsilon_n}$ for $1 \le m \le n \le \ell$ such that~$m = 1$ or~$\varepsilon_{m-1} = -1$, and $n = \ell$ or $\varepsilon_{n+1} = 1$ (and similarly for the set of top substrings~$\Sigma_\top(\sigma)$).

%These sets satisfy the following properties.
%These sets, illustrated in Fig.~\ref{fig:exmProjections}, satisfy the following properties.
%
%\begin{figure}[t]
%	\centerline{
%	\begin{overpic}[scale=.5]{exmProjections}
%			\put(30,6){$\longleftarrow$}
%			\put(31,8){$\projDown$}
%			\put(68,6){$\longrightarrow$}
%			\put(69,8){$\projUp$}
%			\put(12,-3){$\projDown(S)$}
%			\put(50,-3){$S$}
%			\put(85,-3){$\projUp(S)$}
%	\end{overpic}
%	}
%	\vspace{.3cm}
%	\caption{A biclosed set of strings~$S$ (middle) with~$\projDown(S)$ (left) and~$\projUp(S)$~(right). For readibility, $\projUp(S)$ is only partially drawn: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
%	\label{fig:exmProjections}
%\end{figure}

@@

For example, if~$\bar Q$ is an oriented path with no relation, $\equiv$ is a Cambrian congruence of the weak~order~\cite{Reading-CambrianLattices}.
The congruence classes of~$\equiv$ appear as blue rectangles~in~Fig.~\ref{fig:exmLatticeQuotient}.

@@

Coming back to our original problem, we now aim to show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the quotient of the lattice of biclosed set~$\Bicl{\bar Q}$ of Sec.~\ref{subsec:biclosedSets} by the lattice congruence of Sec.~\ref{subsec:congruence}.
The next two propositions provide explicit maps between biclosed sets of strings and non-kissing facets illustrated in Fig.~\ref{fig:exmSurjection}. These maps extend previous definitions of~\cite{McConville} for grid quivers.

@@

\vspace{-.5cm}

\begin{proposition}
For any facet~$F \in \NKC$, the set of strings~$\zeta(F) \! \eqdef \! \displaystyle\closure{\Big( \!\!\bigcup\limits_{\omega \in F} \! \Sigma_\bottom(\omega) \! \Big)}
$~is~biclosed.
\end{proposition}

\vspace{-.2cm}
When the quiver is an oriented path with no relation, the map~$\eta$ should be thought of as the map from permutations to triangulations defined in~\cite{Reading-CambrianLattices}.
Conversely, $\zeta$ maps a triangulation to the minimal permutation in its fiber under~$\eta$.
For the straight quiver, $\eta$ plays the role of the binary search tree insertion while~$\zeta$ selects the minimal linear extension of a binary tree.
%
Using these maps, we show that the increasing flip graph on non-kissing facets is isomorphic to the Hasse diagram of the lattice quotient~$\Bicl{\bar Q}/{\equiv}$.
